%% Master CV - Cristian Uscata Garcia
%% Comprehensive overview of all competencies, experience, and achievements.
%% Use as a master reference when tailoring role-specific CVs (cv/main_<company>.tex).
%%
%% Compile with: lualatex main_example.tex
%% (pdflatex often fails on modern MiKTeX with fontawesome5 font-expansion errors.)

\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{blue}

% Force both first and last name AND section headings to render in moderncv
% blue (color1). Default banking on lualatex+MiKTeX leaves these black, which
% looks inconsistent with the rest of the blue accent scheme.
\renewcommand*{\firstnamestyle}[1]{{\fontsize{34}{36}\bfseries\upshape\color{color1}#1}}
\renewcommand*{\lastnamestyle}[1]{{\fontsize{34}{36}\bfseries\upshape\color{color1}#1}}
\renewcommand*{\sectionstyle}[1]{{\sectionfont\color{color1}#1}}

\usepackage[utf8]{inputenc}
\usepackage{needspace}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=blue,
    pdftitle={Cristian Uscata - CV},
    pdfpagemode=FullScreen,
}
\usepackage[scale=0.80]{geometry}
\usepackage{import}

% personal data
\name{Cristian}{Uscata}
\address{Lima, Peru}{}{}
\phone[mobile]{(+51) 965 373 728}
\email{crisuscata@gmail.com}
\extrainfo{\href{https://www.linkedin.com/in/crisuscata}{LinkedIn} $\cdot$ Remote (UTC-5)}

\begin{document}

\makecvtitle

% ============================================================
%     PROFILE STATEMENT
% ============================================================

\vspace{6pt}
\small{Senior Software Engineer with 10+ years building scalable, high-performance backend systems in Java. Proven track record leading end-to-end legacy-to-microservices migrations with Spring Boot and AWS across banking, government, and healthcare. Experienced with event-driven and real-time data platforms (Kafka, Spark), and comfortable owning architecture and integration standards while mentoring engineers in distributed, English-speaking teams.}

% ============================================================
%     CORE COMPETENCIES
% ============================================================

\section{Core Competencies}
\vspace{1pt}
\begin{itemize}

\item \textbf{Backend \& Core}: Java, Spring Boot, Spring Security, Microservices, RESTful APIs, DDD, SOA.

\item \textbf{Cloud \& DevOps}: AWS (S3, EC2, DynamoDB, RDS), Docker, Kubernetes, CI/CD (GitLab, Jenkins), Terraform, Shell Scripting.

\item \textbf{Event Streaming \& Data}: Kafka, RabbitMQ, Event-Driven Architecture, Apache Spark, Hadoop, Scala.

\item \textbf{Frontend \& Databases}: Angular, React, JavaScript, TypeScript; MongoDB, Oracle, SQL Server.

\item \textbf{Ways of Working}: TDD, Agile, Scrum, mentoring, defining technical standards; agentic coding with Claude Code.

\end{itemize}

% ============================================================
%     PROFESSIONAL EXPERIENCE
% ============================================================

\section{Professional Experience}
\vspace{3pt}
\begin{itemize}

% --- Most Recent Role ---
\needspace{5\baselineskip}
\item{\cventry{Feb 2025--Present}{Senior Software Engineer}{MINCETUR (Ministry of Foreign Trade \& Tourism)}{Lima, Peru}{}{\vspace{1pt}
\begin{itemize}
    \item Backend development and platform work for public-sector systems using Java and Spring Boot.
\end{itemize}}}

\vspace{3pt}

\needspace{5\baselineskip}
\item{\cventry{Apr 2024--Feb 2025}{Senior Software Engineer}{Comptroller General of the Republic (Contralor\'ia General)}{Peru}{}{\vspace{1pt}
\begin{itemize}
    \item Led the end-to-end migration of a critical legacy system to a modern microservices architecture using Java and Spring Boot, enhancing scalability and maintainability.
    \item Developed high-performance backend services and APIs, collaborating with the Architecture team to define standards and seamless integrations with data-processing layers.
\end{itemize}}}

\vspace{3pt}

\needspace{5\baselineskip}
\item{\cventry{2023--2024}{Senior Software Engineer}{Scotiabank}{LATAM}{}{\vspace{1pt}
\begin{itemize}
    \item Designed and optimized high-performance, low-latency APIs and backend services using Java and AWS, with secure data-exchange protocols.
    \item Resolved performance bottlenecks integrating complex third-party data systems; led a legacy modernization using Docker and Angular.
\end{itemize}}}

\vspace{3pt}

\needspace{5\baselineskip}
\item{\cventry{2021--2023}{Software Engineer}{Qualifacts}{USA}{}{\vspace{1pt}
\begin{itemize}
    \item Drove migration from a monolithic platform to a scalable microservices architecture, increasing deployment velocity and resilience.
    \item Built core backend services and APIs with Java, Spring Boot, and AWS, integrating Apache Kafka for high-volume real-time streaming.
    \item Collaborated with Architecture and Data Engineering teams on standards for data integrity and reliability.
\end{itemize}}}

\vspace{3pt}

\needspace{5\baselineskip}
\item{\cventry{2020--2021}{Senior Java FullStack}{Zoluxiones}{Peru}{}{\vspace{1pt}
\begin{itemize}
    \item Developed microservices and full-stack solutions using Java, Spring, Angular, and AWS.
    \item Defined project scopes and mentored junior developers.
\end{itemize}}}

\vspace{3pt}

\needspace{5\baselineskip}
\item{\cventry{2018--2020}{Senior Software Engineer}{SUNAT (National Tax Authority)}{Peru}{}{\vspace{1pt}
\begin{itemize}
    \item Built integration components with IBM tools, Docker, and Kubernetes.
    \item Developed real-time data-processing modules using Kafka, MongoDB, Hadoop, and Scala serving 1M+ users.
\end{itemize}}}

\vspace{3pt}

\needspace{5\baselineskip}
\item{\cventry{2017--2018}{Software Engineer}{Teamsoft SAC}{Peru}{}{\vspace{1pt}
\begin{itemize}
    \item Led major data migration and integration efforts across multiple customer applications.
    \item Reduced operational risk by 90\% through automation and process standardization.
\end{itemize}}}

\vspace{3pt}

\needspace{5\baselineskip}
\item{\cventry{2012--2016}{Software Developer}{PCM}{Peru}{}{\vspace{1pt}
\begin{itemize}
    \item Designed a core system for automated banking processes, eliminating manual tasks.
    \item Delivered 10+ production-ready projects with focus on maintainability and scalability.
\end{itemize}}}

\end{itemize}

% ============================================================
%     EDUCATION
% ============================================================

\section{Education}
\vspace{1pt}
\begin{itemize}

\needspace{3\baselineskip}
\item{\cventry{2007--2011}{Systems Engineering degree (Ingeniero de Sistemas)}{Universidad Nacional del Callao}{Peru}{}{}}

\end{itemize}

% ============================================================
%     LANGUAGES
% ============================================================

\section{Languages}
\vspace{1pt}
\begin{itemize}
\item Spanish (native), English (advanced / professional working proficiency).
\end{itemize}

% ============================================================
%     REFERENCES
% ============================================================

\section{References}
\vspace{1pt}
\begin{itemize}
\item{Available upon request.}
\end{itemize}

\end{document}
